### 2013-07-11 mcmc.tex
troubleshooting section notes

@@

>>>>

\section{Troubleshooting}

...Run on standard distributons.

...Set likelihood to 1 and check that you sample your prior pdf.

...Low acceptance fraction?  Reducing step size \emph{must} increase fraction.

...Appearance of good and bad chains (show examples).

...Different initializations leading to different posterior samplings?

...Jammed ensemble sampler?

...Degeneracies and duplications in parameter space; reparameterizations.

@@

...How to deal with forbidden regions in prior, or sharp prior boundaries?

...How to deal with constraints that pin you to a subspace of the parameter space?  Method-dependent.
